---
title: "Psy-BAANC Methodological Factors Pipeline"
output: html_notebook
---
```{r}
# Load necessary libraries
library(lme4)   # for linear mixed effects models
library(dplyr)  # for data manipulation
library(MuMIn) # for R squared
library(lmerTest) # for model comparison
```

# Step 1: Clean & process data

```{r}
# Load data frame with all experimental meta data

meta = read.csv("/media/data01/processed/private_data/behavior/250211_metadata.csv")
```

```{r}
# Split the dataframe into smaller dataframes based on 'expt' column

splits <- split(meta, meta$experiment)
```

```{r}
# Function "clean_experiment_data" to remove all columns w/ blank value or constant value columns

clean_experiment_data <- function(expt_list) {
  # Initialize an empty list to store cleaned data frames
  cleaned_list <- list()

  # Iterate over each experiment and its data frame
  for (expt_name in names(expt_list)) {
    df <- expt_list[[expt_name]]  # Extract the data frame for the current experiment
    
    # Identify columns that are entirely blank (NA) or constant across all rows
    cols_to_remove <- sapply(df, function(col) {
      # Check if the column is entirely NA or has only one unique value
      all_na <- all(is.na(col))
      all_same_value <- length(unique(col)) == 1
      return(all_na || all_same_value)
    })
    
    # Remove the columns that are entirely blank or have the same value
    cleaned_df <- df[, !cols_to_remove]
    
    # Store the cleaned data frame back into the list
    cleaned_list[[expt_name]] <- cleaned_df
  }

  # Return the updated list with cleaned data frames
  return(cleaned_list)
}

# Clean the data frames
cleaned_splits <- clean_experiment_data(splits)
```

```{r}
# Function "process_column_types" assigns each meta variable its appropriate value type, as a numeric or a factor

process_column_types <- function(cleaned_expt_list) {
  # Define the columns that should be numeric or factor
  numeric_columns <- c( "age", "weight", "timepoint", "handling", "injections", "acclimation", "h_wall", "L", "L1_3C", "L2_3C", "w", "h_floor", "center_defined",  "d_FST", "d1_NOR", "d2_NOR", "novel_object_area", "novel_object_height", "familiar_object_area", "familiar_object_height", "social_cup_baseArea", "social_cup_height", "water_depth", "other_mice", "prior_expts", "cagemates", "percent_open", "percent_center", "velocity", "d3_immobility", "d1_immobility", "delta_immobility","social_score", "discrimination_index", "avg_time_exploring", "htr_total", "social_preference_score", "time_social_pre", "time_social_post", "social_cond_mice", "tone_frequency", "tone_amplitude", "percent_freezing_retrieval", "percent_freezing_ex1", "percent_freezing_ex2")   
  factor_columns <- c("mouse_ID", "cage_ID", "institution", "lab", "treatment", "sex", "analysis", "exptr_sex", "epm_lip","expt_time", "counterbalanced_object_location", "counterbalanced_cup_location", "juv_or_no_ovary", "same_treatment", "pip_vs_pure", "expt_time_enc", "expt_time_retr", "expt_time_ex1", "expt_time_ex2")  

  # Initialize an empty list to store processed data frames
  processed_list <- list()

  # Iterate over each experiment data frame in the cleaned list
  for (expt_name in names(cleaned_expt_list)) {
    df <- cleaned_expt_list[[expt_name]]  # Extract the cleaned data frame

    # Convert columns to numeric where appropriate
    for (col_name in numeric_columns) {
      if (col_name %in% names(df)) {
        df[[col_name]] <- as.numeric(df[[col_name]])
      }
    }

    # Convert columns to factor where appropriate
    for (col_name in factor_columns) {
      if (col_name %in% names(df)) {
        df[[col_name]] <- as.factor(df[[col_name]])
      }
    }

    # Store the processed data frame in the result list
    processed_list[[expt_name]] <- df
  }

  # Return the updated list of processed data frames
  return(processed_list)
}

# Process the data frames
processed_splits <- process_column_types(cleaned_splits)
```

# Step 2: Create Linear Mixed Effects Models

```{r}
# Function "create_lme_formula" creates an lme formula and returns it as a list with the expt name, and the formula

create_lme_formula <- function(expt_list, expt_name, y_value) {
  
  # Define possible fixed effects column names
  # Modify based on your needs
  
  fixed_effects_candidates <- c("treatment", "sex",  "age", "weight", "handling", "acclimation", "L", "w", "epm_lip",  "d_FST", "d1_NOR", "d2_NOR", "water_depth", "other_mice", "juv_or_no_ovary",  "cagemates", "tone_frequency", "tone_amplitude", "social_cond_mice","pip_vs_pure","injections", "h_wall", "h_floor", "center_defined", "same_treatment","expt_time", "prior_expts", "timepoint" )  
  # , "expt_time_enc", "expt_time_retr", "expt_time_ex1", "expt_time_ex2",   remove or add for Fear Conditioning
  
  # Retrieve the data frame for the specified experiment
  df <- expt_list[[expt_name]]
  
  # Find columns that match the fixed effects candidates
  fixed_effects <- intersect(fixed_effects_candidates, colnames(df))
  
  # Ensure the y_value is included in the data frame
  if (!y_value %in% colnames(df)) {
    stop(paste("The specified y_value column", y_value, "is not in the data frame"))
  }
  
  # Construct the fixed effects part of the formula
  fixed_formula <- paste(fixed_effects, collapse = " + ")
  
  # If there are any fixed effects, combine them with the y_value (dependent variable)
  if (length(fixed_effects) > 0) {
    formula <- paste(y_value, "~", fixed_formula)
  } else {
    formula <- paste(y_value, "~ 1")  # Only intercept if no fixed effects found
  }
  
  # Add random effects: cage_ID nested within lab
  random_effects <- "(1 | lab/cage_ID)"
  
  # Final formula: combine fixed and random effects
  final_formula <- as.formula(paste(formula, random_effects, sep = " + "))
  
  # Return a list with the experiment name and the corresponding formula
  return(final_formula)
}
```

```{r}
# Function "fit_lme_model" to create and fit a linear mixed-effects model using lme4, uses function "create_lme_formula" to get the proper formula

fit_lme_model <- function(expt_list, expt_name, y_value) {
  
  # Get the formula using the existing create_lme_formula function
  formula_info <- create_lme_formula(expt_list, expt_name, y_value)
  
  # Retrieve the data for the specified experiment
  df <- expt_list[[expt_name]]
  
  # Fit the linear mixed-effects model using lme4::lmer
  model <- lme4::lmer(formula_info, data = df)
  
  # Return the fitted model
  return(model)
}
```

## HTR
### y = head twitch count

```{r}
# multivariate
htr <- fit_lme_model(processed_splits, "HTR", "htr_total")

# random effects
htr_null <- lme4::lmer(htr_total ~ 1 + (1 | lab/cage_ID), processed_splits$HTR)

# Rx only
htr_Rx <- lme4::lmer(htr_total ~ treatment + (1 | lab/cage_ID), processed_splits$HTR)
```

## aOFT
### y = % time in center

```{r}
# multivariate
aOFT_percent_center <- fit_lme_model(processed_splits, "aOFT", "percent_center")
# random effects
aOFT_percent_center_null <- lme4::lmer(percent_center ~ 1 + (1 | lab/cage_ID), processed_splits$aOFT)
# Rx only
aOFT_percent_center_Rx <- lme4::lmer(percent_center ~ treatment + (1 | lab/cage_ID), processed_splits$aOFT)
```

### y = velocity (cm/s)

```{r}
# multivariate
aOFT_velocity <- fit_lme_model(processed_splits, "aOFT", "velocity")
# random effects
aOFT_velocity_null <- lme4::lmer(velocity ~ 1 + (1 | lab/cage_ID), processed_splits$aOFT)
# Rx only
aOFT_velocity_Rx <- lme4::lmer(velocity ~ treatment + (1 | lab/cage_ID), processed_splits$aOFT)
```

## pOFT
### y = % time in center

```{r}
# multivariate
pOFT_percent_center <- fit_lme_model(processed_splits, "pOFT", "percent_center")
# random effects
pOFT_percent_center_null <- lme4::lmer(percent_center ~ 1 + (1 | lab/cage_ID), processed_splits$pOFT)
# Rx only
pOFT_percent_center_Rx <- lme4::lmer(percent_center ~ treatment + (1 | lab/cage_ID), processed_splits$pOFT)
```

### y = velocity (cm/s)

```{r}
# multivariate
pOFT_velocity <- fit_lme_model(processed_splits, "pOFT", "velocity")
# random effects
pOFT_velocity_null <- lme4::lmer(velocity ~ 1 + (1 | lab/cage_ID), processed_splits$pOFT)
# Rx only
pOFT_velocity_Rx <- lme4::lmer(velocity ~ treatment + (1 | lab/cage_ID), processed_splits$pOFT)
```

## aNOE
### y = average time spent exploring novel object

```{r}
# multivariate
aNOE_avg_time_exploring <- fit_lme_model(processed_splits, "aNOE", "avg_time_exploring")
# random effects
aNOE_avg_time_exploring_null <- lme4::lmer(avg_time_exploring ~ 1 + (1 | lab/cage_ID), processed_splits$aNOE) 
# Rx only
aNOE_avg_time_exploring_Rx <- lme4::lmer(avg_time_exploring ~ treatment + (1 | lab/cage_ID), processed_splits$aNOE)
```

## pNOE
### y = average time spent exploring novel object

```{r}
# multivariate
pNOE_avg_time_exploring <- fit_lme_model(processed_splits, "pNOE", "avg_time_exploring")
# random effects
pNOE_avg_time_exploring_null <- lme4::lmer(avg_time_exploring ~ 1 + (1 | lab/cage_ID), processed_splits$pNOE) 
# Rx only
pNOE_avg_time_exploring_Rx <- lme4::lmer(avg_time_exploring ~ treatment + (1 | lab/cage_ID), processed_splits$pNOE)
```

## aEPM
### y = % time in open arms

```{r}
# multivariate
aEPM_percent_open <- fit_lme_model(processed_splits, "aEPM", "percent_open")
# random effects
aEPM_percent_open_null <- lme4::lmer(percent_open ~ 1 + (1 | lab/cage_ID), processed_splits$aEPM) 
# Rx only
aEPM_percent_open_Rx <- lme4::lmer(percent_open ~ treatment + (1 | lab/cage_ID), processed_splits$aEPM)
```

## pEPM
### y = % time in open arms

```{r}
# multivariate
pEPM_percent_open <- fit_lme_model(processed_splits, "pEPM", "percent_open")
# random effects
pEPM_percent_open_null <- lme4::lmer(percent_open ~ 1 + (1 | lab/cage_ID), processed_splits$pEPM) 
# Rx only
pEPM_percent_open_Rx <- lme4::lmer(percent_open ~ treatment + (1 | lab/cage_ID), processed_splits$pEPM)
```

## aSIT
### y = social preference score

```{r}
# multivariate
aSIT_social_score <- fit_lme_model(processed_splits, "aSIT", "social_score")
# random effects
aSIT_social_score_null <- lme4::lmer(social_score ~ 1 + (1 | lab/cage_ID), processed_splits$aSIT) 
# Rx only
aSIT_social_score_Rx <- lme4::lmer(social_score ~ treatment + (1 | lab/cage_ID), processed_splits$aSIT)
```

## pSIT
### y = social preference score

```{r}
# multivariate
pSIT_social_score <- fit_lme_model(processed_splits, "pSIT", "social_score")
# random effects
pSIT_social_score_null <- lme4::lmer(social_score ~ 1 + (1 | lab/cage_ID), processed_splits$pSIT)
# Rx only
pSIT_social_score_Rx <- lme4::lmer(social_score ~ treatment + (1 | lab/cage_ID), processed_splits$pSIT)
```

## rFST
### y = time spent immobile

```{r}
# multivariate
rFST_d3_immobility <- fit_lme_model(processed_splits, "rFST", "d3_immobility")
# random effects
rFST_d3_immobility_null <- lme4::lmer(d3_immobility ~ 1 + (1 | lab/cage_ID), processed_splits$rFST)
# Rx only
rFST_d3_immobility_Rx <- lme4::lmer(d3_immobility ~ treatment + (1 | lab/cage_ID), processed_splits$rFST)
```

## rTST
### y = time spent immobile

```{r}
# multivariate
rTST_d3_immobility <- fit_lme_model(processed_splits, "rTST", "d3_immobility")
# random effects
rTST_d3_immobility_null <- lme4::lmer(d3_immobility ~ 1 + (1 | lab/cage_ID), processed_splits$rTST)
# Rx only
rTST_d3_immobility_Rx <- lme4::lmer(d3_immobility ~ treatment + (1 | lab/cage_ID), processed_splits$rTST)
```

## pTST
### y = time spent immobile

```{r}
# multivariate
pTST_d1_immobility <- fit_lme_model(processed_splits, "pTST", "d1_immobility")
# random effects
pTST_d1_immobility_null <- lme4::lmer(d1_immobility ~ 1 + (1 | lab/cage_ID), processed_splits$pTST)
# Rx only
pTST_d1_immobility_Rx <- lme4::lmer(d1_immobility ~ treatment + (1 | lab/cage_ID), processed_splits$pTST)
```

## sCPP
### y = social preference score

```{r}
# multivariate
sCPP <- fit_lme_model(processed_splits, "sCPP", "social_preference_score")
# random effects
sCPP_null <- lme4::lmer(social_preference_score ~ 1 + (1 | lab/cage_ID), processed_splits$sCPP)
# Rx only
sCPP_Rx <- lme4::lmer(social_preference_score ~ treatment + (1 | lab/cage_ID), processed_splits$sCPP)
```

## preFC
### y = % freezing retrieval

```{r}
# multivariate
preFC_retr <- fit_lme_model(processed_splits, "preFC", "percent_freezing_retrieval")
# random effects
preFC_retr_null <- lme4::lmer(percent_freezing_retrieval ~ 1 + (1 | lab/cage_ID), processed_splits$preFC)
# Rx only
preFC_retr_Rx <- lme4::lmer(percent_freezing_retrieval ~ treatment + (1 | lab/cage_ID), processed_splits$preFC)
```

### y = % freezing extinction 1

```{r}
# multivariate
preFC_ex1 <- fit_lme_model(processed_splits, "preFC", "percent_freezing_ex1")
# random effects
preFC_ex1_null <- lme4::lmer(percent_freezing_ex1 ~ 1 + (1 | lab/cage_ID), processed_splits$preFC)
# Rx only
preFC_ex1_Rx <- lme4::lmer(percent_freezing_ex1 ~ treatment + (1 | lab/cage_ID), processed_splits$preFC)
```

### y = % freezing extinction 2

```{r}
# multivariate
preFC_ex2 <- fit_lme_model(processed_splits, "preFC", "percent_freezing_ex2")
# random effects
preFC_ex2_null <- lme4::lmer(percent_freezing_ex2 ~ 1 + (1 | lab/cage_ID), processed_splits$preFC)
# Rx only
preFC_ex2_Rx <- lme4::lmer(percent_freezing_ex2 ~ treatment + (1 | lab/cage_ID), processed_splits$preFC)
```

## postFC
### y = % freezing extinction 1

```{r}
# multivariate
postFC_ex1 <- fit_lme_model(processed_splits, "postFC", "percent_freezing_ex1")
# random effects
postFC_ex1_null <- lme4::lmer(percent_freezing_ex1 ~ 1 + (1 | lab/cage_ID), processed_splits$postFC)
# Rx only
postFC_ex1_Rx <- lme4::lmer(percent_freezing_ex1 ~ treatment + (1 | lab/cage_ID), processed_splits$postFC)
```

### y = % freezing extinction 2

```{r}
# multivariate
postFC_ex2 <- fit_lme_model(processed_splits, "postFC", "percent_freezing_ex2")
# random effects
postFC_ex2_null <- lme4::lmer(percent_freezing_ex2 ~ 1 + (1 | lab/cage_ID), processed_splits$postFC)
# Rx only
postFC_ex2_Rx <- lme4::lmer(percent_freezing_ex2 ~ treatment + (1 | lab/cage_ID), processed_splits$postFC)
```

# Step 3: Model Statistics

```{r}
# Create CSV of experiment confidence intervals

# Function to create 95% confidence interval CSV file
confint95_csv <- function(expt_list, expt_name, y_value) {
  
  # Get the model using the existing fit_lme_model function
  model <- fit_lme_model(expt_list, expt_name, y_value)
  
  # Retrieve the confidence interval
  confint_output <- confint(model, level = 0.95)
  
  # Create a dynamic file name using the variable name
  file_name <- paste0("/media/data01/processed/private_data/behavior/confint_95_", expt_name, "_", y_value, ".csv")
  
  # Fit the linear mixed-effects model using lme4::lmer
  write.csv(confint_output, file =  file_name)
}

# Function to create 99% confidence interval CSV file
confint99_csv <- function(expt_list, expt_name, y_value) {
  
  # Get the model using the existing fit_lme_model function
  model <- fit_lme_model(expt_list, expt_name, y_value)
  
  # Retrieve the confidence interval
  confint_output <- confint(model, level = 0.99)
  
  # Create a dynamic file name using the variable name
  file_name <- paste0("/media/data01/processed/private_data/behavior/confint_99_", expt_name, "_", y_value, ".csv")
  
  # Fit the linear mixed-effects model using lme4::lmer
  write.csv(confint_output, file =  file_name)
}

# Function to create 999% confidence interval CSV file
confint999_csv <- function(expt_list, expt_name, y_value) {
  
  # Get the model using the existing fit_lme_model function
  model <- fit_lme_model(expt_list, expt_name, y_value)
  
  # Retrieve the confidence interval
  confint_output <- confint(model, level = 0.999)
  
  # Create a dynamic file name using the variable name
  file_name <- paste0("/media/data01/processed/private_data/behavior/confint_999_", expt_name, "_", y_value, ".csv")
  
  # Fit the linear mixed-effects model using lme4::lmer
  write.csv(confint_output, file =  file_name)
}
```

## Example w/ HTR 
```{r}
# Get 95% confidence interval for coefficients in multivariate model
# (saves to files)
confint95_csv(processed_splits, "HTR", "htr_total")

# Get the marginal and conditional R squared
r.squaredGLMM(htr)

# Get model statistic summary
summary(htr)

# Get p-value for Rx only model comparing to null model (random effects model)
anova(htr_Rx, htr_null)

# Calculate ICC from variance components of the random effects model
summary(htr_null)
```

# Z-score

```{r}
# Function "z_score_mice_by_lab" z-scores each lab's data using mean_saline_F and SD_saline_F to z-score the female data, and mean_saline_M and SD_saline_M to z-score the male data

z_score_mice_by_lab <- function(df, y_value) {
  
  # Create an empty column for z-scores
  df$z_score <- NA
  
  # Get the unique labs
  labs <- unique(df$lab)
  
  # Loop over each lab to perform the z-scoring for each subset
  for (lab in labs) {
    
    # Subset the data for the current lab
    lab_data <- df[df$lab == lab, ]
    
    # Subset data based on treatment and sex for the current lab
    male_s_mice <- lab_data[lab_data$treatment == "S" & lab_data$sex == "M", ]
    female_s_mice <- lab_data[lab_data$treatment == "S" & lab_data$sex == "F", ]
    
    # Calculate mean and SD for male and female mice with treatment S in this lab
    male_s_mean <- mean(male_s_mice[[y_value]], na.rm = TRUE)
    male_s_sd <- sd(male_s_mice[[y_value]], na.rm = TRUE)
    
    female_s_mean <- mean(female_s_mice[[y_value]], na.rm = TRUE)
    female_s_sd <- sd(female_s_mice[[y_value]], na.rm = TRUE)
    
    # Z-score for males in this lab
    df$z_score[df$lab == lab & df$sex == "M"] <- (df[[y_value]][df$lab == lab & df$sex == "M"] - male_s_mean) / male_s_sd
    
    # Z-score for females in this lab
    df$z_score[df$lab == lab & df$sex == "F"] <- (df[[y_value]][df$lab == lab & df$sex == "F"] - female_s_mean) / female_s_sd
  }
  
  # Return the updated data frame
  return(df)
}
```

## Create df
```{r}
## Create z-score df using the function z_score_mice_by_lab
z_HTR_df <- z_score_mice_by_lab(processed_splits$HTR, "htr_total")
z_aOFT_df <- z_score_mice_by_lab(processed_splits$aOFT, "percent_center")
z_aOFTv_df <- z_score_mice_by_lab(processed_splits$aOFT, "velocity")
z_pOFT_df <- z_score_mice_by_lab(processed_splits$pOFT, "percent_center")
z_pOFTv_df <- z_score_mice_by_lab(processed_splits$pOFT, "velocity")
z_aEPM_df <- z_score_mice_by_lab(processed_splits$aEPM, "percent_open")
z_pEPM_df <- z_score_mice_by_lab(processed_splits$pEPM, "percent_open")
z_aNOE_df <- z_score_mice_by_lab(processed_splits$aNOE, "avg_time_exploring")
z_pNOE_df <- z_score_mice_by_lab(processed_splits$pNOE, "avg_time_exploring")
z_rFST_df <- z_score_mice_by_lab(processed_splits$rFST, "d3_immobility")
z_rTST_df <- z_score_mice_by_lab(processed_splits$rTST, "d3_immobility")
z_pTST_df <- z_score_mice_by_lab(processed_splits$pTST, "d1_immobility")
z_aSIT_df <- z_score_mice_by_lab(processed_splits$aSIT, "social_score")
z_pSIT_df <- z_score_mice_by_lab(processed_splits$pSIT, "social_score")
z_sCPP_adult_df <- z_score_mice_by_lab(processed_splits$sCPP, "social_preference_score")
z_preFC_retr <- z_score_mice_by_lab(processed_splits$preFC, "percent_freezing_retrieval")
z_preFC_ex1 <- z_score_mice_by_lab(processed_splits$preFC, "percent_freezing_ex1")
z_preFC_ex2 <- z_score_mice_by_lab(processed_splits$preFC, "percent_freezing_ex2")
z_postFC_ex1 <- z_score_mice_by_lab(processed_splits$postFC, "percent_freezing_ex1")
z_postFC_ex2 <- z_score_mice_by_lab(processed_splits$postFC, "percent_freezing_ex2")
```

## Create models

```{r}
z_HTR_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_HTR_df)
z_HTR_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_HTR_df)

z_aOFT_percent_center_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_aOFT_df)
z_aOFT_percent_center_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_aOFT_df)
z_aOFTv_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_aOFTv_df)
z_aOFTv_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_aOFTv_df)

z_pOFT_percent_center_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_pOFT_df)
z_pOFT_percent_center_null <- lmer(z_score ~1 + (1 | lab/cage_ID), z_pOFT_df)
z_pOFTv_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_pOFTv_df)
z_pOFTv_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_pOFTv_df)

z_aEPM_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_aEPM_df)
z_aEPM_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_aEPM_df)

z_pEPM_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_pEPM_df)
z_pEPM_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_pEPM_df)

z_aNOE_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_aNOE_df)
z_aNOE_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_aNOE_df)

z_pNOE_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_pNOE_df)
z_pNOE_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_pNOE_df)

z_rFST_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_rFST_df)
z_rFST_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_rFST_df)

z_rTST_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_rTST_df)
z_rTST_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_rTST_df)

z_pTST_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_pTST_df)
z_pTST_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_pTST_df)

z_aSIT_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_aSIT_df)
z_aSIT_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_aSIT_df)

z_pSIT_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_pSIT_df)
z_pSIT_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_pSIT_df)

z_sCPP_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_sCPP_adult_df)
z_sCPP_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_sCPP_adult_df)

z_preFC_retr_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_preFC_retr)
z_preFC_retr_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_preFC_retr)

z_preFC_ex1_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_preFC_ex1)
z_preFC_ex1_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_preFC_ex1)

z_preFC_ex2_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_preFC_ex2)
z_preFC_ex2_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_preFC_ex2)

z_postFC_ex1_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_postFC_ex1)
z_postFC_ex1_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_postFC_ex1)

z_postFC_ex2_Rx <- lmer(z_score ~ treatment + (1 | lab/cage_ID), z_postFC_ex2)
z_postFC_ex2_null <- lmer(z_score ~ 1 + (1 | lab/cage_ID), z_postFC_ex2)
```
## Model statistics, example w/ HTR

```{r}
# Get the marginal and conditional R squared
r.squaredGLMM(z_HTR_Rx)

# Get model statistic summary
summary(z_HTR_Rx)

# Get p-value for Rx only model comparing to null model (random effects model)
anova(z_HTR_Rx, z_HTR_null)

# Calculate ICC from variance components of the random effects model
summary(z_HTR_null)
```


